Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-07-17 cordillera-cycle.tex
Add parameter table.

@@

% tab:records
\begin{table*}[t]
  \caption{Extrema of ice volume and extent corresponding to MIS~4, 3 and 2 for
           each of the low-resolution simulations (Fig.~\ref{fig:timeseries}).}
  \label{tab:extrema}
  {\begin{tabular}{l*{3}{|ccc}}
    \tophline
             & \multicolumn{3}{c}{Age (ka)}
             & \multicolumn{3}{c}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m~s.l.e.)} \\
    Record   &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    GRIP     & -57.58 & -49.24 & -19.52
             &   1.98 &   0.46 &   2.13
             &   7.52 &   0.89 &   8.52 \\
    NGRIP    & -60.26 & -50.16 & -22.85
             &   2.16 &   0.50 &   2.09
             &   8.69 &   0.93 &   8.24 \\
    EPICA    & -61.87 & -45.57 & -17.10
             &   1.57 &   0.95 &   2.08
             &   5.20 &   2.44 &   8.35 \\
    Vostok   & -60.87 & -49.68 & -16.87
             &   1.55 &   0.86 &   2.14
             &   5.10 &   2.01 &   8.66 \\
    ODP 1012 & -55.41 & -47.08 & -23.21
             &   1.44 &   0.85 &   2.13
             &   4.50 &   2.06 &   8.46 \\
    ODP 1020 & -60.16 & -52.24 & -29.46
             &   1.32 &   0.70 &   2.08
             &   3.88 &   1.52 &   8.32 \\
    \middlehline
    Minimum  & -61.87 & -52.24 & -29.46
             &   1.32 &   0.46 &   2.08
             &   3.88 &   0.89 &   8.24 \\
    Maximum  & -55.41 & -45.57 & -16.87
             &   2.16 &   0.95 &   2.14
             &   8.69 &   2.44 &   8.66 \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

>>>>

% tab:params
\begin{table*}
  \centering
  \caption{Main parameters of the ice sheet model.
           \todo{At the moment, this is pretty extensive (does not fit on one
                 page using the standard font size). There are probably a
                 couple of things that are not needed here, like for instance
                 the very standard things (gravity, gas constant, etc). Many
                 parameters are not defined in the text. Do we need to
                 introduce them, or should we skip them? I wonder if the last
                 column is needed, in which case it needs to be completed.}}
  \label{tab:params}
  \footnotesize
  {\begin{tabular}{llrll}
    \tophline
    Not.    & Name & Value & Unit & Source \\
    \middlehline

    \multicolumn{2}{l}{\emph{Ice rheology}} \\

    $\rho$  & Ice density
            & 910
            & \unit{kg\,m^{-3}}
            & \citet{Aschwanden.etal.2012} \\

    $g$     & Standard gravity
            & 9.81
            & \unit{m\,s^{-2}}
            & \citet{Aschwanden.etal.2012} \\

    $n$     & Glen exponent
            & 3
            & -
            & \aref \\

    $A_c$   & Ice hardness coefficient cold
            & $3.61\times10^{-13}$
            & \unit{Pa^{-3}\,s^{-1}}
            & \citet{Paterson.Budd.1982} \\

    $A_w$   & Ice hardness coefficient warm
            & $1.73\times10^3$
            & \unit{Pa^{-3}\,s^{-1}}
            & \citet{Paterson.Budd.1982} \\

    $Q_c$   & Flow law activation energy cold
            & $6.0\times10^4$
            & \unit{J\,mol^{-1}}
            & \citet{Paterson.Budd.1982} \\

    $Q_w$   & Flow law activation energy warm
            & $13.9\times10^4$
            & \unit{J\,mol^{-1}}
            & \citet{Paterson.Budd.1982} \\

    $R$     & Ideal gas constant
            & 8.31441
            & \unit{J\,mol^{-1}\,K^{-1}}
            & \aref \\

    $T_c$   & Flow law critical temperature
            & 263.15
            & \unit{K}
            & \citet{Paterson.Budd.1982} \\

    $f$     & Flow law water fraction coeff.
            & 181.25
            & -
            & \citet{Lliboutry.Duval.1985} \\

    $\beta$ & Clapeyron constant
            & $7.9\times10^{-8}$
            & \unit{K\,Pa^{-1}}
            & \citet{Luthi.etal.2002} \\

    $c_i$   & Ice specific heat capacity
            & 2009
            & \unit{J\,kg^{-1}\,K^{-1}}
            & \citet{Aschwanden.etal.2012} \\

    $c_w$   & Water specific heat capacity
            & 4170
            & \unit{J\,kg^{-1}\,K^{-1}}
            & \citet{Aschwanden.etal.2012} \\

    $k$     & Ice thermal conductivity
            & 2.10
            & \unit{J\,m^{-1}\,K^{-1}\,s^{-1}}
            & \citet{Aschwanden.etal.2012} \\

    $L$     & Water latent heat of fusion
            & $3.34\times10^5$
            & \unit{J\,kg^{-1}\,K^{-1}}
            & \citet{Aschwanden.etal.2012} \\

    \multicolumn{2}{l}{\emph{Basal sliding}} \\

    $q$     & Pseudo-plastic sliding exponent
            & 0.25
            & -
            & - \\

    $v_{th}$& Pseudo-plastic threshold velocity
            & 100.0
            & \unit{m\,yr^{-1}}
            & - \\

    $c_0$   & Till cohesion
            & 0.0
            & Pa
            & - \\

    $\delta$& Effective pressure coefficient
            & 0.02
            & -
            & - \\

    $e_0$   & Till reference void ratio
            & 0.69
            & -
            & \citet{Tulaczyk.etal.2000} \\

    $C_c$   & Till compressibility coefficient
            & 0.12
            & -
            & \citet{Tulaczyk.etal.2000} \\

    $W_{max}$ & Maximal till water thickness
            & 2.0
            & m
            & - \\

    \multicolumn{2}{l}{\emph{Bedrock and lithosphere}} \\

    $\rho_b$& Bedrock density
            & 3300
            & \unit{kg\,m^{-3}}
            & \aref \\

    $c_b$   & Bedrock specific heat capacity
            & 1000
            & \unit{J\,kg^{-1}\,K^{-1}}
            & \citet{Ritz.1997} \\

    $k_b$   & Bedrock thermal conductivity
            & 3.0
            & \unit{J\,m^{-1}\,K^{-1}\,s^{-1}}
            & \citet{Ritz.1997} \\

    $\nu_m$ & Mantle viscosity
            & $1\times10^21$
            & \unit{Pa\,s}
            & \citet{Lingle.Clark.1985} \\

    $\rho_l$& Lithosphere density
            & 3300
            & \unit{kg\,m^{-3}}
            & \citet{Lingle.Clark.1985} \\

    $D$     & Lithosphere flexural rigidity
            & $5.0\times10^24$
            & \unit{N}
            & \citet{Lingle.Clark.1985} \\

    \multicolumn{2}{l}{\emph{Surface and atmosphere}} \\

    $T_s$   & Temperature of snow precipitation
            & 273.15
            & \unit{K}
            & \aref \\

    $T_r$   & Temperature of rain precipitation
            & 275.15
            & \unit{K}
            & \aref \\

    $F_s$   & Degree-day factor for ice
            & $3.04\times10^{-3}$
            & \unit{m\,K^{-1}\,day^{-1}}
            & \citet{Shea.etal.2009} \\

    $F_i$   & Degree-day factor for ice
            & $4.59\times10^{-3}$
            & \unit{m\,K^{-1}\,day^{-1}}
            & \citet{Shea.etal.2009} \\

    $\gamma$& Air temperature lapse-rate
            & $6\times10^{-3}$
            & \unit{K\,m{-1}}
            & - \\

    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

@@

% tab:extrema
\begin{table*}[t]
  \caption{Extrema of ice volume and extent corresponding to MIS~4, 3 and 2 for
           each of the low-resolution simulations (Fig.~\ref{fig:timeseries}).}
  \label{tab:extrema}
  {\begin{tabular}{l*{3}{|ccc}}
    \tophline
             & \multicolumn{3}{c}{Age (ka)}
             & \multicolumn{3}{c}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m~s.l.e.)} \\
    Record   &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    GRIP     & -57.58 & -49.24 & -19.52
             &   1.98 &   0.46 &   2.13
             &   7.52 &   0.89 &   8.52 \\
    NGRIP    & -60.26 & -50.16 & -22.85
             &   2.16 &   0.50 &   2.09
             &   8.69 &   0.93 &   8.24 \\
    EPICA    & -61.87 & -45.57 & -17.10
             &   1.57 &   0.95 &   2.08
             &   5.20 &   2.44 &   8.35 \\
    Vostok   & -60.87 & -49.68 & -16.87
             &   1.55 &   0.86 &   2.14
             &   5.10 &   2.01 &   8.66 \\
    ODP 1012 & -55.41 & -47.08 & -23.21
             &   1.44 &   0.85 &   2.13
             &   4.50 &   2.06 &   8.46 \\
    ODP 1020 & -60.16 & -52.24 & -29.46
             &   1.32 &   0.70 &   2.08
             &   3.88 &   1.52 &   8.32 \\
    \middlehline
    Minimum  & -61.87 & -52.24 & -29.46
             &   1.32 &   0.46 &   2.08
             &   3.88 &   0.89 &   8.24 \\
    Maximum  & -55.41 & -45.57 & -16.87
             &   2.16 &   0.95 &   2.14
             &   8.69 &   2.44 &   8.66 \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}
